Thesis - Upwelling and MHW/Cold spells analyses

### 2019-09-03 SST_patterns.Rmd
update

```{r}
load("Data/site_list_sub.Rdata")
load("Data/SACTN_US.RData")
load("Data/site_pixels.RData")
load("Data/OISST.RData")
```

@@

```{r}
ncDir <- "/home/amieroh/Documents/Data/Datasets/MUR/daily"
csvDir <- "/home/amieroh/Documents"

@@

# apply the function
system.time(llply(ncList, read_nc, region = "BC", csvDir = csvDir, .parallel = TRUE))
```

@@

@@

ncDir <- "/Volumes/Challenger_Deep/OceanData/CMC0.2deg-CMC-L4-GLOB-v2.0/netCDF"
CMC.csv.dir <- "/Volumes/Challenger_Deep/spatial/processed/CMC0.2deg-CMC-L4-GLOB-v2.0/WBC/daily"
```

@@

pixel_match <- sat_pixels %>% 
  group_by(product) %>% 
  nest() %>% 
  mutate(match = purrr:::map(data, match_func)) %>% 
  select(-data) %>%
  unnest(match)

>>>>

```{r}
load("Data/site_list_sub.Rdata")
load("Data/SACTN_US.RData")
load("Data/site_pixels.RData")
load("Data/OISST.RData")
OISST <- BC_avhrr_only_v2_Document_Document 
rm(BC_avhrr_only_v2_Document_Document )
```

@@

```{r}
library(stringr)
library(tidyverse)
library(reshape2)
library(ncdf4) # library for processing netCDFs
library(plyr)
library(lubridate)
library(data.table)
library(doMC); doMC::registerDoMC(cores = 7)

# nc_data <- nc_open('/home/amieroh/Documents/Data/Datasets/MUR/daily/20020601-JPL-L4UHfnd-GLOB-v01-fv04-MUR.nc')
# print(nc_data)

ncDir <- "/home/amieroh/Documents/Data/Datasets/MUR/daily"
csvDir <- "/home/amieroh/Documents"

@@

read_nc <- function(ncDir = ncDir, csvDir = csvDir) 
  ncList <- list.files(path = paste0(ncDir), pattern = "*.nc", full.names = TRUE, include.dirs = TRUE)
  ncFirst <- head(list.files(path = paste0(ncDir, "/"), pattern = "*.nc", full.names = FALSE), 1)
  ncLast <- tail(list.files(path = paste0(ncDir, "/"), pattern = "*.nc", full.names = FALSE), 1)
  strtDate <- str_sub(ncFirst, start = 1, end = 8)
  endDate <- str_sub(ncLast, start = 1, end = 8)

  ncFun <- function(ncFile = ncFile, csvDir = csvDir) {
    nc <- nc_open(ncFile)
    pathLen <- nchar(paste0(ncDir, "/")) + 1
    fNameStem <-
      substr(basename(ncFile), 10, 38)
    fDate <- substr(basename(ncFile), 1, 8)
    sst <- ncvar_get(nc, varid = "analysed_sst") %>%
      round(4)
    dimnames(sst) <- list(lon = nc$dim$lon$vals,
                          lat = nc$dim$lat$vals)
    nc_close(nc)
    sst <- as_tibble(melt(sst, value.name = "temp"))
    sst$t <- ymd(fDate)
    na.omit(sst)
    fwrite(sst,
           file = paste0(csvDir, "/", fNameStem, "-", strtDate, "-", endDate, ".csv"),
           append = TRUE, col.names = FALSE)
    rm(sst)
  }

llply(ncList, ncFun, csvDir = csvDir, .parallel = TRUE)
```

@@

#          1         2         3         4
# 12345678901234567890123456789012345678901

@@

ncDir <- "/Volumes/Challenger_Deep/OceanData/CMC0.2deg-CMC-L4-GLOB-v2.0/netCDF"
```

@@

pixel_match <- OISST %>% 
  group_by(product) %>% 
  nest() %>% 
  mutate(match = purrr:::map(data, match_func)) %>% 
  select(-data) %>%
  unnest(match)

### 2019-09-03 Write_up/write_up.Rmd
update

In order to compare abiotic variables such as wind action and direction along the South African coastline, large historical datasets for temperature, chlorophyll-a and wind were analysed and accessed.

@@

## Chlorophyll-a data

In order to observe the patterns in the variation of the chlorophyll-a concentration with the intensity and duration of upwelling events,  MODIS-Aqua Chlorophyll a concentration, OCI Algorithm, 8-day composite were used. The National Aeronautics and Space Administration’s (NASA) Moderate Resolution imaging Spectroradiometer (MODIS) Aqua satellite is an example of a satellite currently collecting the reflected wavelength energy from the earth. The MODIS Aqua satellite records wavelength data down to the 1% photosynthetically available depth (0.1 PAR depth) of the water column, a vital component in the estimation of chlorophyll (NASA.GOV, http://oceancolor.gsfc.nasa.gov). Because chlorophyll-a concentration retrieval is only possible over cloud-free areas the daily data offered may have large data gaps due to cloud cover. The quality of the chlorophyll-a concentration  estimates depends strongly on the quality of the cloud mask. The NASA Aqua satellite contains the MODIS sensor that is used for detecting chlorophyll-a concentrations (ocean color) in the world's oceans, among other applications (NASA.GOV, http://oceancolor.gsfc.nasa.gov). The Level 3 standard mapped image (SMI) chlorophyll-a dataset has a monthly temporal resolution and 4.6 km spatial resolution. The SMI dataset is an image representation of binned MODIS data.

>>>>

In order to compare abiotic variables such as wind action and direction along the South African coastline, large historical datasets for temperature and wind were analysed and accessed.

@@
